Effects of Antenna Beam Chromaticity on Redshifted 21~cm Power Spectrum and Implications for Hydrogen Epoch of Reionization Array

### 2016-05-09 ForegroundSimulations/ms.tex
Minor edits to ms.tex and response to referee
From d2876cc (fgsim):
====================

(*) coverletter.txt to git repo

In ms.tex,

(*) make minor corrections

In reply_to_referee_report.tex,

(*) Fine-tune response to referee report

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{f1.eps}
  \caption{{\bf 19-element HERA layout used in this study, a subset of the full proposed 350-element layout. It is located in the South African Karoo Radio Astronomy Reserve.}}
  \label{fig:HERA-19}
\end{figure}

@@

{\bf Equations~\ref{eqn:obsvis} and \ref{eqn:delay-transform} define} the interplay between foregrounds and antenna power pattern, and the mapping between geometric phases of baselines and delays. We discuss the spillover of foreground power beyond the horizon delay limits caused by the chromatic nature of the antenna power pattern.

@@

We estimate the worst case EoR-foreground dynamic range in the $\boldsymbol{b}$--$\alpha$ parameter space as:
\begin{align}
  \rho(\boldsymbol{b},f_0,\alpha) &= \min_{|k_\parallel|>k_\parallel^\textrm{FA}(\boldsymbol{b})}\left\{\frac{P_\textrm{H{\sc i}}(|\boldsymbol{b}|,k_\parallel,f_0)}{P_\textrm{FG}(\boldsymbol{b},k_\parallel,f_0,\alpha)}\right\}.
\end{align}
This denotes the minimum EoR-foreground dynamic range in $k_\parallel$-modes of interest for {\it foreground avoidance}, $|k_\parallel| > k_\parallel^\textrm{FA}(\boldsymbol{b})$, for each baseline vector ($\boldsymbol{b}$), subband ($f_0$), and sky pointing ($\alpha$).

@@

\begin{figure*}[htb]
  % \centering
  % \subfloat[][EoR model 1, 150~MHz subband ]{\label{fig:21cmfast-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_150.0_MHz_subband.eps}}
  % \subfloat[][EoR model 2, 150~MHz subband ]{\label{fig:lidz-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_150.0_MHz_subband.eps}} \\
  % \subfloat[][EoR model 1, 170~MHz subband ]{\label{fig:21cmfast-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_170.0_MHz_subband.eps}}
  % \subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_170.0_MHz_subband.eps}}
  \subfloat[][EoR model 1, 150~MHz subband ]{\label{fig:21cmfast-fg-ratio-150}\includegraphics[width=0.45\linewidth]{f8a.eps}}
  \subfloat[][EoR model 2, 150~MHz subband ]{\label{fig:lidz-fg-ratio-150}\includegraphics[width=0.45\linewidth]{f8b.eps}} \\
  \subfloat[][EoR model 1, 170~MHz subband ]{\label{fig:21cmfast-fg-ratio-170}\includegraphics[width=0.45\linewidth]{f8c.eps}}
  \subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{f8d.eps}}
  \caption{Worst case EoR-foreground dynamic range, $\rho(\boldsymbol{b},f_0,\alpha)$, in {\it foreground avoidance} modes for different HERA-19 baselines as a function of RA ($\alpha$) of pointing on the sky. Each panel corresponds to the EoR model and subband indicated. The baseline vector is specified by its length (in m) and orientation (in degrees) at the bottom and top of the $x$-axis respectively. The color scale is logarithmic. Even in the worst case, HERA will be able detect EoR drawn from independent models on all baselines for a large fraction of a full 24~hour sky transit cycle {\bf except during the transit of the Galactic plane seen at 16--19 hours of RA}. $\rho(\boldsymbol{b},f_0,\alpha)$ is seen to increase with increasing baseline length. This is because the loss in sensitivity to diffuse foreground power with increase in antenna spacings is faster than in the case of the EoR signal.}
  \label{fig:eor-fg-ratios}
\end{figure*}

@@

In all four cases considered here, except when the Galactic {\bf plane} appears overhead {\bf roughly between 16 and 19 hours of RA}, the worst case signal-foreground ratio lies above unity in most of this parameter space. It demonstrates that HERA should detect the EoR signal with a very high signal-foreground ratio on all baselines over a majority of the pointings.

>>>>

\begin{figure}[htb]
  \centering
  \includegraphics[width=\linewidth]{f1.eps}
  \caption{{\bf 19-element HERA layout used in this study, a subset of the full proposed 350-element layout. It is located in the South African Karoo Radio Astronomy Reserve. Each dish is 14~m across. The relative physical scale is illustrated by the group of people in this picture.}}
  \label{fig:HERA-19}
\end{figure}

@@

{\bf Equations~\ref{eqn:obsvis} and \ref{eqn:delay-transform} define} the interplay between foregrounds, {\bf the} antenna power pattern, and the mapping between geometric phases of baselines and delays. We discuss the spillover of foreground power beyond the horizon delay limits caused by the chromatic nature of the antenna power pattern.

@@

We estimate the worst-case EoR-foreground dynamic range in the $\boldsymbol{b}$--$\alpha$ parameter space as:
\begin{align}
  \rho(\boldsymbol{b},f_0,\alpha) &= \min_{|k_\parallel|>k_\parallel^\textrm{FA}(\boldsymbol{b})}\left\{\frac{P_\textrm{H{\sc i}}(|\boldsymbol{b}|,k_\parallel,f_0)}{P_\textrm{FG}(\boldsymbol{b},k_\parallel,f_0,\alpha)}\right\}.
\end{align}
This denotes the minimum EoR-foreground dynamic range in $k_\parallel$-modes of interest for {\it foreground avoidance}, $|k_\parallel| > k_\parallel^\textrm{FA}(\boldsymbol{b})$, for each baseline vector ($\boldsymbol{b}$), subband ($f_0$), and sky pointing ($\alpha$).

@@

\begin{figure*}[htb]
  % \centering
  % \subfloat[][EoR model 1, 150~MHz subband ]{\label{fig:21cmfast-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_150.0_MHz_subband.eps}}
  % \subfloat[][EoR model 2, 150~MHz subband ]{\label{fig:lidz-fg-ratio-150}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_150.0_MHz_subband.eps}} \\
  % \subfloat[][EoR model 1, 170~MHz subband ]{\label{fig:21cmfast-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_21cmfast_chrmbeam_sim_170.0_MHz_subband.eps}}
  % \subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{eor_fg_ratio_llim_lidz_chrmbeam_sim_170.0_MHz_subband.eps}}
  \subfloat[][EoR model 1, 150~MHz subband ]{\label{fig:21cmfast-fg-ratio-150}\includegraphics[width=0.45\linewidth]{f8a.eps}}
  \subfloat[][EoR model 2, 150~MHz subband ]{\label{fig:lidz-fg-ratio-150}\includegraphics[width=0.45\linewidth]{f8b.eps}} \\
  \subfloat[][EoR model 1, 170~MHz subband ]{\label{fig:21cmfast-fg-ratio-170}\includegraphics[width=0.45\linewidth]{f8c.eps}}
  \subfloat[][EoR model 2, 170~MHz subband ]{\label{fig:lidz-fg-ratio-170}\includegraphics[width=0.45\linewidth]{f8d.eps}}
  \caption{Worst-case EoR-foreground dynamic range, $\rho(\boldsymbol{b},f_0,\alpha)$, in {\it foreground avoidance} modes for different HERA-19 baselines as a function of RA ($\alpha$) of pointing on the sky. Each panel corresponds to the EoR model and subband indicated. The baseline vector is specified by its length (in m) and orientation (in degrees) at the bottom and top of the $x$-axis respectively. The color scale is logarithmic. Even in the worst case, HERA will be able detect EoR drawn from independent models on all baselines for a large fraction of a full 24~hour sky transit cycle {\bf except during the transit of the Galactic plane seen at 16--19 hours of RA}. $\rho(\boldsymbol{b},f_0,\alpha)$ is seen to increase with increasing baseline length. This is because the loss in sensitivity to diffuse foreground power with increase in antenna spacings is faster than in the case of the EoR signal.}
  \label{fig:eor-fg-ratios}
\end{figure*}

@@

In all four cases considered here, except when the Galactic {\bf plane} appears overhead {\bf roughly between 16 and 19 hours of RA}, the worst-case signal-foreground ratio lies above unity in most of this parameter space. It demonstrates that HERA should detect the EoR signal with a very high signal-foreground ratio on all baselines over a majority of the pointings.
